The responses of \textit{\textit{Spinifex littoreus}} to sand burial on the coastal area of Pingtan Island, Fujian Province, South China

### 2020-12-28 tex/interactcsesample.tex
change figs' number

After a 20-day sand burial experiment, we found that the ramet height of \textit{S. littoreus} did not show any significant difference compared with the control group (CG). However, there were significant effects on the growth of horizontal stolons in both half-intense sand burial (HI) and complete-intense sand burial (CI) treatments, particularly the latter (Figure~\ref{fig:lattice}). 
Specifically, the significant effect of sand burial on the stolon growth was firstly observed at 9 days for the CI treatments, while it delayed at 13 days for the HI treatments ($P<0.05$).
Moreover, the growth of horizontal stolons was more enhanced by sand burial in CI treatments than HI treatments, with the stolon length increased by $40.79\%$ in CI treatments, while $24.56\%$ in HI treatments after the end of 20-day sand burial experiment (Figure~\ref{fig:growth}a and B).
Based on that, the proportion of stolon length in top section was increased continuously from $22.09\%$, $25.53\%$ to $46.48\%$, $50.20\%$, for HI and CI treatments, respectively.

@@

% 大多数的人工沙埋不同程度上促进了不定根的生成，无论是不定根数量还是总长度（Fig3）。
The production of adventitious roots was promoted in most of the sand burial treatments, both in total length and number of roots. The most increase was observed in the HM treatments, and the average root length is $5.1cm$, the average root number is $2$, while no adventitious roots were observed in the CG treatments (Figure~\ref{fig:roots}a and B).
% 而且不定根主要分布在基部，顶端无不定根生成。
The adventitious roots were mainly occurred at the base section of stolons (96\%), and few (4\%) were found at the middle section, while no adventitious roots were found at top sections (Figure~\ref{fig:roots}C).
% 经过20天的沙埋实验，老鼠楽植株茎和叶片的干重比例在不同程度上发生了改变。
The dry weight ratio between stems and leaves of \textit{S. littoreus} was decreased under most of the sand burial treatments compared with the CG treatments, and varied in different sections of stolons. More biomass was allocated to leaves, particularly for the top section of stolons (Figure~\ref{fig:ratio}).

>>>>

After a 20-day sand burial experiment, we found that the ramet height of \textit{S. littoreus} did not show any significant difference compared with the control group (CG). However, there were significant effects on the growth of horizontal stolons in both half-intense sand burial (HI) and complete-intense sand burial (CI) treatments, particularly the latter (Figure~\ref{fig:lattice}). 
Specifically, the significant effect of sand burial on the stolon growth was firstly observed at 9 days for the CI treatments, while it delayed at 13 days for the HI treatments ($P<0.05$).
Moreover, the growth of horizontal stolons was more enhanced by sand burial in CI treatments than HI treatments, with the stolon length increased by $40.79\%$ in CI treatments, while $24.56\%$ in HI treatments after the end of 20-day sand burial experiment (Figure~\ref{fig:growth} A and B).
Based on that, the proportion of stolon length in top section was increased continuously from $22.09\%$, $25.53\%$ to $46.48\%$, $50.20\%$, for HI and CI treatments, respectively.

@@

% 大多数的人工沙埋不同程度上促进了不定根的生成，无论是不定根数量还是总长度（Fig3）。
The production of adventitious roots was promoted in most of the sand burial treatments, both in total length and number of roots. The most increase was observed in the HM treatments, and the average root length is $5.1cm$, the average root number is $2$, while no adventitious roots were observed in the CG treatments (Figure~\ref{fig:roots} A and B).
% 而且不定根主要分布在基部，顶端无不定根生成。
The adventitious roots were mainly occurred at the base section of stolons (96\%), and few (4\%) were found at the middle section, while no adventitious roots were found at top sections (Figure~\ref{fig:roots}C).
% 经过20天的沙埋实验，老鼠楽植株茎和叶片的干重比例在不同程度上发生了改变。
The dry weight ratio between stems and leaves of \textit{S. littoreus} was decreased under most of the sand burial treatments compared with the CG treatments, and varied in different sections of stolons. More biomass was allocated to leaves, particularly for the top section of stolons (Figure~\ref{fig:ratio}).
